Intentional release of native species undermines ecological stability

### 2022-10-05 rmd/manuscript.Rmd
Update manuscript.Rmd

As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive release (**Figure 1B**). The effect was striking in its magnitude, almost doubling the CV at the highest release level. Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S8**). This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S6-S8** for full statistics). In the meantime, the SDs had vague relationships with intentional release (**Figures 1B and 2**).

>>>>

As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with intensive release (**Figure 1B**). The effect was striking in its magnitude, almost doubling the CV at the highest release level. Our analysis strongly supported the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta %>% filter(response == "cv") %>% pull(prob), 2)` (**Table S6**). This pattern was associated with the reduced long-term average of the total community density and fewer taxonomic richness (**Figures 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figures 1B and 2;** see **Tables S6-S8** for full statistics). In the meantime, the SDs had vague relationships with intentional release (**Figures 1B and 2**).
